Methods for Large Scale Learning to Rank

### 2014-11-13 report/Chapters/Introduction.tex
nieuw puntje dolf

Some research has been done in the area of parallel or distributed machine learning \cite{Chu2007,Chang2007}. However, almost none of these studies include the Learning to Rank sub-field of machine learning. The field of efficient Learning to Rank has been getting some attention lately \cite{Asadi2013a,Asadi2013b,Busa-Fekete2012,Sousa2012,Shukla2012}, since Liu \cite{Liu2007} first stated its growing importance back in 2007. Only a few of these studies \cite{Sousa2012,Shukla2012} have explored the possibilities of efficient Learning to Rank through the use of parallel programming paradigms.\\

>>>>

Some research has been done in the area of parallel or distributed machine learning \cite{Chu2007,Chang2007}, with the aim to speed-up machine learning computation or to increase the size of the data sets that can be processed with machine learning techniques. However, almost none of these parallel or distributed machine learning studies target the Learning to Rank sub-field of machine learning. The field of efficient Learning to Rank has received some attention lately \cite{Asadi2013a,Asadi2013b,Busa-Fekete2012,Sousa2012,Shukla2012}, since Liu \cite{Liu2007} first stated its growing importance back in 2007. Only a few of these studies \cite{Sousa2012,Shukla2012} have explored the possibilities of efficient Learning to Rank through the use of parallel programming paradigms.\\
